\section{Introduction}
The Requirement Analysis and Specification Document (RASD) aims to focus on the tasks needed to develop and implement an application, taking account of the requirements of the involved stakeholders and, analyzing and documenting also the application requirements.\\
Then, in the second part of the document, there is a more formal definition of the requirements with the use of the Alloy language.\\
In general this document is meant for developers tasked with the implementation of the System and also for all the other entities involved in validation and managing of the project.

\subsection{Purpose}
\textit{SafeStreets} is an application that was created with the intention of monitoring the compliance with traffic regulations. Its goal is to allow Users to notify traffic violations, collect those data about them, elaborate into information, and then provide them to both Users or authorities who need, for aiming different scopes. \\ \\
The application provides Users a way to send data about a violation (most common are parking violations ones, e.g. vehicles parked in reserved places), like the kind of violation, pictures of the involved vehicles, and the date and the position in which the violation occurred. The User can also specify the license plate of the vehicle and the name of the street, but in case he/she doesn't, the application is equipped with algorithms capable to obtain those and other metadata by pictures and position.\\\\
SafeStreets stores all these data, received ones and computed ones, and allows Users and competent authorities to access them, in order to gather useful information about traffic and violations, e.g. areas with the higher number of violations. This could, for example, help municipality to identify areas in which they must watch over.\\\\
Moreover, the System is also able to combine its own data, with data provided by municipality authorities, in case they offer a service that provides them. Basing on the information obtained in this way, SafeStreets will give suggestions about how to improve urban mobility situation, or about how to prevent some kind of violations from being committed (e.g. putting some cameras in vulnerable areas, add some kind of barrier and so on).\\\\
For last, authorities are allowed to use information provided by the application and generate traffic tickets. This leads the application to having to implement a method for ensuring the integrity of the incriminating data, from when the data is generated, to when it is delivered to the application. Authorities have to be sure, for example, that they're not giving a fine to a vehicle just because of a picture alteration has been carried out by a notifying User, so altered information must be discarded. SafeStreets will also use statistics on those "rotten" data with the aim to do measure on number of bad Users, or to monitor the reliability and effectiveness of the application it self. \\\\

Here below are listed out the goals we did talk about:

\begin{itemize}
\item {[G.1]} Allows User and Authority to access the functionalities of the application from different locations and devices.
\item {[G.2]} Allows the User to notify about traffic violations.
\item {[G.3]} Allows the User to send pictures, type of the violation, GPS and time.
\item {[G.4]} Must compute the license plate and the address where the violation occurred, from the received data.
\item {[G.5]} Allows Authority to check the correctness of a report.
\item {[G.6]} Allows Authority to generate traffic tickets from verified reports.
\item {[G.7]} Allows both User and Authority to access information about unsafe areas.
\item {[G.8]} Allows both User and Authority to access statistics about effectiveness of SafeStreets.
\item {[G.9]} Allows both User and Authority to access statistics about violations.
\item {[G.10]} Must cross its data with the municipality ones in order to provide suggestions to improve urban mobility.
\item {[G.11]} Must ensure that corrupted information are discarded.


\end{itemize}

\subsection{Scope}
    According to the World and Machine paradigm, introduced by M. Jackson and P. Zave. We can idenfity the Machine as the System to be developed and the environment in which SafeStreets will be used as the World. The separation between these two concepts allow us to classify the entire phenomena in three different types.
    \vspace{0.5cm}
    
    % to be fixed vspace
    
    \noindent\textbf{World phenomena}, events that take place in the real world and that the machine cannot observe.
    \begin{itemize}
      \item The driver has an accident and leaves the car in an inappropriate place.
      \item A malicious user reports a fake traffic violation.
      \item A user has an old mobile phone with a low quality camera.
      \item Movement of a user from a position to another one before sending the picture.
      \item Unexpected connection losses before the User sends a picture.
    \end{itemize}
    \vspace{0.5cm}
    
    \noindent\textbf{Machine phenomena}, events that take place inside the \textit{System} and cannot be observed by the real world.
    \begin{itemize}
      \item Encryption of sensitive data.
      \item All operations performed to store/retrieve collected data.
      \item The System retrieves information about unsafe areas from municipalities' services.
    \end{itemize}
    \vspace{0.5cm}
    
    \noindent\textbf{Shared phenomena:}\\\newline
    Controlled by the world and observed by the machine.
    \begin{itemize}
      \item A guest can sign up to the application or log in if is already registered.
      \item The User can send report traffic violations at any time.
     \item The User can add further information in order to help authorities.
      \item The Municipality offers up-to-date information about accidents on the territory.
    \end{itemize}
    
    \vspace{10px}
    
    \noindent{Controlled by the machine and observed by the World.}
    \begin{itemize}
      \item The System allows the Authorities to access to violation reports.
      \item The System allows users to view own reports.
      \item The System shows inferred safe/unsafe areas.
      \item The Municipality gets suggestions generated by the System.
      \item The System notifies Authorities about corrupted pictures.
      \item The User can view Statistics built by the System.
      \item The System manages multiple reports of the same traffic violation.
    \end{itemize}

\subsection{Definitions, Acronyms, Abbreviations}
    \subsubsection{Definitions}
        \begin{itemize}
            \item \textbf{Guest}: a person who has not logged in or registered yet and cannot use the functionalities of the System.
            \item \textbf{User}: a person that uses the application to send notifications of traffic violations.
            \item \textbf{Authority}: a municipality representative that is able to create traffic tickets depending on the violation that a person has committed.
            \item \textbf{Data provided by Municipality}: all the information sent by Municipality to Safestreets in order to infer suggestions.
            \item \textbf{Sensitive data}: any kind of information that could be used to identify the User who reported a traffic violation.
            \item \textbf{Unsafe areas}: areas in which a high number of traffic violations took place.
            \item \textbf{Statistics}: information that allows to show specific data, for example the offender who has committed the highest number of violations, the safest area, the number of tickets that are being generated and so on.
        \end{itemize}
        
    \subsubsection{Acronyms}
    \begin{itemize}
        \item UI: User Interface
        \item API: Application User Interface
        \item S2B: System to Be Developed
    \end{itemize}
    \subsubsection{Abbreviations}
        \begin{itemize}
            \item {[\textbf{G.i}]} : i-th goal.
            \item {[\textbf{D.i}]} : i-th domain assumption.
            \item {[\textbf{R.i}]}: i-th functional requirement.
            \item {[\textbf{UCi}]}: i-th use case.
        \end{itemize}

%  HISTORY TABLEEEEEEEEEE###############  

\subsection{Revision history}


\begin{center}
\begin{tabular}{| c | c | m{5.5cm} | m{5.3cm} |}
	\hline
	Version & Date & Authors & \textbf{Summary}\\
	\hline
	1.0 & 10/11/2019 & \begin{tabular}{@{}c@{}}Iacopo Marri\\Manuel Salamino\\Steven Alexander Salazar Molina\end{tabular} & First release \\
	\hline
	1.1 & 09/12/2019 & \begin{tabular}{@{}c@{}}Iacopo Marri\\Manuel Salamino\\Steven Alexander Salazar Molina\end{tabular}   & \parbox{5.3cm}{ \textbf{Changes:} \\
	\begin{itemize}
\item	 Changed some Phenomena.
	\item Made corrections in Product Perspective.
\item 	 Added [D.7].
\item	 Corrections in some Goals.
\item	 A correction in Product Functions. 
\item	 A correction in User Charateristics.
	 

	\end{itemize}
	}\\
	\hline
\end{tabular}
\end{center}






\subsection{Reference
Documents}
    \begin{itemize}
        \item Alloy Documentation
        \item Project assignment specifications
        \item IEEE Standard on Requirement Engineering (ISO/IEC/IEEE 29148) 
        % https://www.iso.org/standard/45171.ht
    \end{itemize}

\subsection{Document
Structure}

\textbf{Section 1} introduces the problem and describes the purpose of the application SafeStreets. Furthermore, describes the scope in which the application is defined by stating the goals and a brief description of phenomena.\\\\
\textbf{Section 2} presents the overall description of the project. \textit{Product Perspective} give more details about the boundaries of the system and world, machine and shared phenomena, while in \textit{Product Functions} are described the main functions of the system and in \textit{User Characteristics} the main actors. At last are defined the domain assumption on which the system relies on.\\\\
\textbf{Section 3} contains all the specific requirements needed to satisfy each goal. Furthermore, are highlighted the major functions and interactions between the actors and the system using use cases and sequence diagrams.\\\\
\textbf{Section 4} shows the alloy model and discuss its purpose.\\\\
\textbf{Section 5} explain the effort spent by each group member to accomplish this project.\\